A mixture of hidden Markov models to predict the lymphatic spread in head and neck cancer

### 2024-01-22 content/manuscript.qmd
rename some var keys & rerun pipeline

In @fig-prevalence-by-subsite, we have plotted the prevalence of involvement in the four LNLs I, II, III, and IV stratified by the primary tumor's subsite. We only included patients with tumors in the gum, floor of mouth, other/unspecified parts of the mouth, palate, oropharynx, tosil, base of tongue, and other/unspecified parts of tongue, resulting in {{< var num_patients >}} patients.

>>>>

In @fig-prevalence-by-subsite, we have plotted the prevalence of involvement in the four LNLs I, II, III, and IV stratified by the primary tumor's subsite. We only included patients with tumors in the gum, floor of mouth, other/unspecified parts of the mouth, palate, oropharynx, tosil, base of tongue, and other/unspecified parts of tongue, resulting in {{< var num_patients.total >}} patients.
